Real-space computation of $E$/$B$-mode maps I: \revisit{Formalism, Compact Kernels, and Polarized Filaments}

### 2018-06-21 articles/formalism/sections/discussion.tex
more discussion edits

The Green's function interpretation provides some useful insights into these operations. This interpretation allows us to think of ${}_{+2}X=Q+iU$ as some spin-2 charge which radiates out a complex spin-0 scalar field $E+iB$. The resulting complex scalar maps can be then understood as arising from superposition of the radiating fields emanating from all the spin charges on the sphere.  The $E/B$ mode maps are merely the real and imaginary parts of this field.  \revisit{A similar equation for real space $E/B$ operators was derived in \cite{Zaldarriaga2001a}, but treated the flat sky case and did not explicitly derive the radial kernel.}

>>>>

The Green's function interpretation provides some useful insights into these operations. This interpretation allows us to think of ${}_{+2}X=Q+iU$ as some spin-2 charge which radiates out a complex spin-0 scalar field $E+iB$. The resulting complex scalar maps can be then understood as arising from superposition of the radiating fields emanating from all the spin charges on the sphere.  The $E/B$ mode maps are merely the real and imaginary parts of this field.  \revisit{A similar equation for real space $E/B$ operators was derived in \cite{Zaldarriaga2001a}, treating the flat sky case and not explicitly deriving the radial kernel.}
